{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-08-15 Notebook LaTEX/Momentum Accelerations/paper.tex
/w\, work home sync

\begin{abstract} 
    \noindent
    Nesterov accelreated gradient method has been in the spotlight for the past decades due its wide spread applications and theories of optimal convergence. 
    Decades later it still opens up new interpretations. 
    Our work suggests a proximal point interpretation of accelerated gradient method for the method of accelerated proximal gradient method as a major extension to the interpretation proposed by Ahn and Sra \cite{ahn_understanding_2022}. 
    The proofs had been streamlined, extended and new error terms are added to allow a larger set of stepsize sequence for the PPM. 
    Additionally, we proposed a line search method to dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in algorithm implementations based on the PPM understanding, with numerical experiments.

@@

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    They explored the interpretation of Nesterov acceleration as a proximal of an upper surrogate function, and then a lower surrogate function. 
    Inspired by such an interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex and friendly to a proximal operator. 
    \par
    Classical analysis and extension of Nesterov accelerated gradient existed. 
    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm. 
    In Ahn's work however, the complexities are packaged into the PPM interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since doesn't have a Moreau envelope. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm however, lead to the valuable insights that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function. 
    \par
    % The paper is organized as follow: 
    % \begin{enumerate}
    %     \item Section 
    % \end{enumerate}

\section{Preliminaries}\label{sec:preliminaries}
    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying assumption 
    \ref*{assumption:smooth-nonsmooth-sum}. 
    A lower bound function is identified using the gradient mapping operator and proved in lemma 
    \ref*{lemma:grad_map_linearization}, 
    this is a key component of the proximal point interpretation of the accelerated gradient method. 
    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth. 
    \end{assumption}

    \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
        Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
        For all $y \in \RR$ it verifies
        $$
            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
            - 
            \left(
                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
            \right)
            \le 
            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
        $$
        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
    \end{theorem}
    \begin{remark}
        We use this theorem to prove the convergence of the proximal point method. 
        See the proof (\cite{bauschke_convex_2017}, theorem 12.26). 
    \end{remark}

@@

    \begin{lemma}[Gradient Mapping Approximates Subgradient]
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref{assumption:smooth-nonsmooth-sum}}, 
        let $\mathcal T_L, \mathcal G_L$ be given by 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}.
        Then for all $x$, the gradient mapping verifies
        \begin{align*}
            x^+ &= \mathcal T_L(x), 
            \\
            \mathcal G_L(x) = L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Using the resolvent definition of the proximal gradient operator and the fact that the single-valuedness in the convex settings, $x^+$ has relations: 
        \begin{align*}
            x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
            \\
            [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
            \\
            x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
            \\
            x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
            \\
            L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
            \\
            L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
            \\
            \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{proof}

@@

    \label{lemma:grad_map_linearization}

@@

        The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}. 

@@

\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
    In this section, we present the PPM formulation of the accelerated proximal gradient method. 
    These interpretations of \cite{ahn_understanding_2022} are extension in the non-smooth context using the proximal gradient mapping operator. 
    The next definition starts the discussion. 
    \begin{definition}[Linear Lower Bounding Function]\label{def:gradmap-linear-lowerbnd-fxn}
        Let $h = f+ g$ satisfies
        \hyperref[assumption:smooth-nonsmooth-sum]{definition \ref*{assumption:smooth-nonsmooth-sum}}, 
        $\mathcal G_L$ given by 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
        Define for all $y$ the function
        \begin{align*}
            l_h(x; y) = h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
            + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2. 
        \end{align*}
    \end{definition} 
    \begin{remark}
        The function satisfies $l_h(x; y) \le h(x)$ for all $x \in \RR, y \in \RR$ by 
        \hyperref[lemma:grad_map_linearization]
        {lemma \ref*{lemma:grad_map_linearization}}. 
    \end{remark}
    \par
    With the above definition, it's possible to formulate a generic form of accelerated gradient method using $l_h(x,y)$ as two proximal point methods anchored at some iterates $x_t, x_{t + 1}$.
    The formulation is generic because of undetermined stepsize parameter $\eta_t, \tilde \eta_t$ from the two proximal point. 
    \par
    We state the PPM interpretation of accelerated gradient in 
    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, 
    which has the equivalent form as presented in
    \hyperref[def:ag_prox_grad_generic]
    {definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[prop:derive_ag_prox_grad_tript]
    {Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
    shows their equivalence. 
    \par
    Throughout this section, we assume 
    \begin{enumerate}
        \item $h=f + g$ satisfies 
            \hyperref[assumption:smooth-nonsmooth-sum]
            {assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
        \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
            \hyperref[def:gradient_mapping]
            {definition \ref*{def:gradient_mapping}}. 
        \item Using all above, let $l_h$ be given by 
            \hyperref[def:gradmap-linear-lowerbnd-fxn]
            {definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
    \end{enumerate}

@@

\section{Generic Lyapunov analysis for Accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
    \par
    The Lypunov function in 
    \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}}
    is identical to Ahn and Sra 
    \cite[section 4.2]{ahn_understanding_2022}, 
    except for the involvement of the gradient mapping. 
    We adapated it into the context of proximal gradient by 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
    \par
    We present the convergence rate by compatifying results into 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
    to assist the proof of  
    \hyperref[thm:generic_ag_convergence]
    {Theorem \ref*{thm:generic_ag_convergence}} 
    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
    \par
    Through out this section, we continue the assumption for $h = f + g$ and gradient mapping $\mathcal G_L$ the same as previous section.

@@

        Setting $z = \mathcal T_L \bar x$, we have the desired results. 

@@

            \right) (h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \N

@@

        If there exists a sequence of $\eta_i, \tilde \eta_i$ as defined in

@@

        Let iterates: $z_t, x_t, y_t$. 

@@

            &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}.

@@

@@

        ) for $t\in \mathbb N$ it has: 

@@

        \ref*{thm:generic_ag_convergence}, 

@@

@@

        By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 

@@

        With this in mind, RHS of $\phi_{t + 1} - \phi_t$ yields: 

@@

@@

        At the last step, we divided both side of the equation by $\tilde \eta_{t + 1} > 0$.

@@

        With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon$ and $\eta_t$.

@@

        Observe that in the case where we choose $\epsilon_t = 0\; \forall t \in \N$, the above relation simplifies to 
            a_{t + 1} &= (1/2)\left(
                1 + \sqrt{1 + 4 c_{t + 1}}
            c_{t + 1} &= a_t^2. 
        This relation is the Famous Nesterov momentum sequence. 
        At the same time, we can analyize the convergence rate of the algorithm by the abstract convergence lemma, producing: 
            &\le \epsilon_{t + 1}\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
        Telescoping yields: 

@@

        Under an ideal case where we wish to attain accelerations, we want $\lim_{T \rightarrow \infty} S_T < \infty$. 

@@

\section{Recovering existing variants of Nesterov accelerated gradient}\label{sec:recovery}
    \subsection{Recovering FISTA}
        From 
        \hyperref[thm:ag_generic_stepsize_constraints]
        {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ is the Nesterov sequence.
        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle, or Similar Triangle Method as referred to by Ahn and Sra.

        \begin{lemma}[Deriving Similar Triangle Form I]
            \quad \\
            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$ 
            in 
                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                y_{t + 1} &= 
                (1 + L\eta_{t + 1})^{-1}
                (
                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                ). 
            It also has an equivalent momentum form 
                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)

@@

            To do, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
            Starting with the former, susbtitute definition of $z_{t + 1}$, $z_{t + 1} = z_t + L^{-1}\nabla f(y_t)$ expanding: 

@@

            So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$
            Reducing it to the classic momentum form starts by 

@@

            This is FISTA by the relation $a_t = 1 + L\eta_t$, hence $(1 + L\eta_{t + 1})^{-1}L\eta_t$ is $(a_t - 1)/a_{t + 1}$.
            Where we proved in 

@@

                {theorem \ref*{thm:ag_generic_stepsize_constraints}}
            that $a_t$ is the Nesterov momentum sequence. 

>>>>

\begin{abstract} 
    \noindent
    Nesterov accelreated gradient method has been in the spotlight for the past decades due its wide spread applications and theories of optimal convergence. 
    Decades later it still opens up new interpretations. 
    Our work suggests a proximal point interpretation of accelerated gradient method for the method of accelerated proximal gradient method as a major extension to the interpretation proposed by Ahn and Sra \cite{ahn_understanding_2022}. 
    The proofs had been streamlined, extended and new error terms are added to allow a larger set of stepsize sequence for the proximal point interpreation. 
    Additionally, we conduct numerical experiment for a line search method that dynamically adjust the strong convexity index $\mu$ and Lipschitz constant of the gradient in for algorithm  using the proximal point understanding of accelerated gradient.

@@

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method applied to an upper surrogate function, and then a lower surrogate function. 
    Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations. 
    \par
    Classical analysis and extension of Nesterov accelerated gradient exist in the literatures. 
    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm. 
    In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since it doesn't have a Moreau envelope. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm however, lead to the valuable insights that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function.

    % \par
    % The paper is organized as follow: 
    % \begin{enumerate}
    %     \item Section 
    % \end{enumerate}

\section{Preliminaries}\label{sec:preliminaries}
    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying 
    \hyperref[assumption:smooth-nonsmooth-sum]
    {assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
    A lower bound function is identified using the gradient mapping operator and proved in
    \hyperref[lemma:grad_map_linearization]{lemma \ref*{lemma:grad_map_linearization}}, 
    this is a key component of the proximal point interpretation of the accelerated gradient method. 
    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth. 
    \end{assumption}

    \begin{theorem}[Proximal Descent Inequality]\label{thm:ppm_descent_ineq}
        Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
        For all $y \in \RR$ it verifies
        $$
            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
            - 
            \left(
                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
            \right)
            \le 
            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
        $$
        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
    \end{theorem}
    \begin{remark}
        We use this theorem to prove the convergence of the proximal point method. 
        The proof can be found in \cite[theorem 12.26]{bauschke_convex_2017}. 
    \end{remark}

@@

    \begin{lemma}[Gradient Mapping Approximates Subgradient]
    \label{lemma:grad-map-approx-subgrad}\; \\
        Suppose $h = f + g$ satisfies 
        \hyperref[assumption:smooth-nonsmooth-sum]{assumption \ref{assumption:smooth-nonsmooth-sum}}, 
        let $\mathcal T_L, \mathcal G_L$ be given by 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}.
        Then for all $x$, the gradient mapping verifies
        \begin{align*}
            x^+ &= \mathcal T_L(x), 
            \\
            \mathcal G_L(x) = L(x - x^+) &\in  \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{lemma}
    \begin{proof}
        Using the resolvent definition of the proximal gradient operator and the fact that the single-valuedness in the convex settings, $x^+$ has relations: 
        \begin{align*}
            x^+ &= [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](x)
            \\
            [I + L^{-1}\partial g](x^+) &\ni [I - L^{-1}\nabla f](x)
            \\
            x^+ + L^{-1}\partial g(x^+) &\ni x - L^{-1}\nabla f(x)
            \\
            x^+ - x + L^{-1}\partial g(x^+) &\ni L^{-1}\nabla f(x)
            \\
            L(x^+ - x) + \partial g(x^+) &\ni - \nabla f(x)
            \\
            L(x - x^+) &\in \nabla f(x) + \partial g(x^+)
            \\
            \mathcal G_L(x) &\in \nabla f(x) + \partial g(x^+). 
        \end{align*}
    \end{proof}

@@

    \label{lemma:grad_map_linearization}\; \\

@@

        The inequality is analogous to \cite[(2.2.57)]{nesterov_lectures_2018}, however Nesterov stated it only for the case when $g$ is an indicator function of some convex set $Q$. 

@@

\section{The PPM interpreation of accelerated gradient}\label{sec:ppm_interp_of_ag}
    In this section, we present the generic PPM formulation of the accelerated proximal gradient method. 
    This is general form presents us with a set of undetermine stepsize parameters $\eta_i, \tilde \eta_i$ that can be changed later to accomodate proofs that take Lypunov functions and phrase the convergence rate using the stepsizes sequence $\tilde \eta_i$. 
    These interpretations are extension in the non-smooth context of Ahn and Sra's work \cite{ahn_understanding_2022} using the proximal gradient mapping operator. 
    The next definition will start the discussion. 
    \begin{definition}[Linear Lower Bounding Function]\label{def:gradmap-linear-lowerbnd-fxn}
        Let $h = f+ g$ satisfies
        \hyperref[assumption:smooth-nonsmooth-sum]{definition \ref*{assumption:smooth-nonsmooth-sum}}, 
        $\mathcal G_L$ given by 
        \hyperref[def:gradient_mapping]{definition \ref*{def:gradient_mapping}}. 
        Define for all $y$ the function
        \begin{align*}
            l_h(x; y) = h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle 
            + \frac{L}{2}\Vert y - \mathcal T_L y\Vert^2. 
        \end{align*}
    \end{definition} 
    \begin{remark}
        The function satisfies $l_h(x; y) \le h(x)$ for all $x \in \RR, y \in \RR$ by 
        \hyperref[lemma:grad_map_linearization]
        {lemma \ref*{lemma:grad_map_linearization}}. 
    \end{remark}
    \par
    With the above definition, it's possible to formulate a generic form of accelerated gradient method using $l_h(x,y)$ as two proximal point methods anchored at some iterates $x_t, x_{t + 1}$.
    The formulation is generic because of undetermined stepsize parameter $\eta_t, \tilde \eta_t$ from the two proximal point. 
    \par
    We state the PPM interpretation of accelerated gradient in 
    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, 
    which has the equivalent form as presented in
    \hyperref[def:ag_prox_grad_generic]
    {definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[prop:derive_ag_prox_grad_tript]
    {Proposition \ref*{prop:derive_ag_prox_grad_tript}} 
    shows their equivalence. 
    \par
    Throughout this section, we assume 
    \begin{enumerate}
        \item $h=f + g$ satisfies 
            \hyperref[assumption:smooth-nonsmooth-sum]
            {assumption \ref*{assumption:smooth-nonsmooth-sum}}, 
        \item Using $h$ as given from above, let $\mathcal T_L, \mathcal G_L$ be given by 
            \hyperref[def:gradient_mapping]
            {definition \ref*{def:gradient_mapping}}. 
        \item Using all above, let $l_h$ be given by 
            \hyperref[def:gradmap-linear-lowerbnd-fxn]
            {definition \ref*{def:gradmap-linear-lowerbnd-fxn}}. 
    \end{enumerate}

@@

\section{Generic Lyapunov analysis for Accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
    \par
    The Lypunov function in 
    \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}}
    is identical to Ahn and Sra 
    \cite[section 4.2]{ahn_understanding_2022}, 
    except for the involvement of the gradient mapping. 
    We adapated it into the context of proximal gradient by 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
    \par
    We present the convergence rate by compatifying results into 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
    to assist the proof of  
    \hyperref[thm:generic_ag_convergence]
    {Theorem \ref*{thm:generic_ag_convergence}} 
    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
    \par
    Throughout the section, we continue the assumption for $h = f + g$, gradient mapping $\mathcal G_L$ and proximal gradient mapping $\mathcal T_L$ from the previous section.

@@

        Setting $z = \mathcal T_L \bar x$, use 
        \hyperref[lemma:grad-map-approx-subgrad]
        {lemma \ref*{lemma:grad-map-approx-subgrad}}, 
        to give the desired results. 

@@

            \right) (h(z_t) - h(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \N,

@@

        If there exists a sequence of $(\eta_i)_{i \in \N}$ as defined in

@@

        Let iterates $z_t, x_t, y_t$ be given by

@@

            \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2.

@@

        Define $\delta_{t + 1} = \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2$. 
        Then the convergence rate stated in 
        \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}
        applies. 

@@

        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}) 
        for $t\in \mathbb N$ it has: 

@@

        {remark \ref*{remark:upsilon-upperbound-for-iterates}}

@@

            \rangle, 

@@

        Because the iterates are produced by 
        vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 

@@

        With this in mind, RHS of $\Phi_{t + 1} - \Phi_t$ yields: 

@@

            \text{divide by } \tilde \eta_{t + 1} > 0

@@

@@

        With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon_t$ and $\eta_t$.

@@

        With $\delta_i$ given by
        \hyperref[thm:generic_ag_convergence]
        {theorem \ref*{thm:generic_ag_convergence}}. 
        Define $\delta_i = \epsilon_{i} \tilde \eta_i$, then 

@@

        Under an ideal case where we wish to attain the best convergence, we want $\lim_{T \rightarrow \infty} S_T < \infty$. 

@@

\section{Recovering existing variants of Nesterov accelerated gradient}\label{sec:recovery}
    In this section, we recovers several variants of the accelerated gradient in the literatures as a special case of 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}, 
    we sate the choice of stepsize parameter $\eta_i, \tilde \eta_i$, verify that they satisfies 
    \hyperref[thm:ag_generic_stepsize_constraints]
    {theorem \ref*{thm:ag_generic_stepsize_constraints}}
    and derive their convergence rate respectively.

    \subsection{Recovering FISTA} 
        Let $\epsilon_i$ be given by
        \hyperref[thm:ag_generic_stepsize_constraints]
        {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ produces the relations 
        \begin{align*}
            a_{t + 1} &= (1/2)\left(
                1 + \sqrt{1 + 4 c_{t + 1}}
            \right), 
            \\
            c_{t + 1} &= a_t^2. 
        \end{align*}
        The recurrenct relations of $a_t$ indicates that it's the famous Nesterov momentum sequence. 
        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle \cite{beck_fast_2009-1}. 
        The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
        \begin{lemma}[Deriving Similar Triangle Form I]
            \quad \\
            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$,
            \hyperref[def:ag_prox_grad_generic]
            {definition \ref*{def:ag_prox_grad_generic}}
            simplifies into 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
                \\
                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                \\
                y_{t + 1} &= 
                (1 + L\eta_{t + 1})^{-1}
                (
                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                ). 
            \end{align*}
            It is also equivalent to 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \\
                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
            \end{align*}
            And this is the FISTA algorithm. 
        \end{lemma}

@@

            Firstly, we show that updates sequence $x_{t + 1} = z_{t + 1} + L\eta_t (z_{t + 1} - z_t)$ is equivalent to $x_{t + 1} = x_t + \tilde\eta_{t + 1}\nabla f(y_t)$. 
            Starting with the former, susbtitute $z_{t + 1} = y_t + L^{-1}\nabla f(y_t)$ as given by 
            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}},
            expanding: 

@@

            So $x_{t + 1} = x_t + \tilde \eta_{t + 1}\mathcal G_L(y_t)$, by assumption $\tilde \eta_{t + 1} = \eta_t + L^{-1}$. 
            Next, consider the updates $y_{t + 1}$ as given by 

@@

            This is FISTA by the relation $a_t = 1 + L\eta_t$ by setting $\epsilon_i = 0$ in

@@

            {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
            making $a_t$ the Nesterov momentum sequence. 
            Observe that $(1 + L\eta_{t + 1})^{-1}L\eta_t$ is $(a_t - 1)/a_{t + 1}$.
            Express using $a_t$, the above algorithm is equivalent to the FISTA algorithm. 
            \par
            By 
            \hyperref[thm:ag_generic_stepsize_constraints]{theorem \ref*{thm:ag_generic_stepsize_constraints}}
            \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}},
            a convergence of $\mathcal O(\sigma_T^{-1})$ is possible. 
            Since $a_t = \tilde \eta_t$, and the Nesterov sequence exhibits $a_{t} \ge (t + 2)/2$, the convergence becomes $\mathcal O(T^{-2})$. 
            It is the optimal convergence rate for all convex functions. 
